Demystifying the Combination of Dynamic Slicing and \\ Spectrum-based Fault Localization

### 2019-02-24 paper/ijcai/paper.tex
another udpate

		\caption{Distribution of $\Delta{}C$ per variant when not considering
		test engineering problems and fault of omissions (left) and only considering
		the cases where \combpar{k} achieved improvement under one of the variants}
		\label{fig:boxplot}
		\vspace{-0.2cm}

@@

In the following, we present statistical analysis to demonstrate that
the distributions of $C$ for each technique are different.
Table~\ref{table:st}, reports the average rank of all faulty
statements of the \dfj{} faults considered to the study after applying both
techniques, \sfl{}$^{k}$ and \combpar{k} for $k=5$ and $k=10$.
In bold, we present the results of the $227$ faults that do not comprise the
cases that are result of the limitations mentioned before (test design and fault of omission). These results show that \ds{} improves \sfl{} in a mean
of $6$ ($3.3\%$ on average) statements on the average ranking of all faulty statements, when considering $k=10$. Inside parentheses, we present the
rank results for all faults which do not report promissing results. However, If we only consider the faults which can benefit from our approach, we can observe that there is a considerable
amount of cases where the approach is actually successful. For
$k=5$, our approach achieves a mean improvement of $41.1$ ($9.57\%$ on average) statements
on the ranking and an impressive maximum ranking improvement
of $3171$ ($96.7\%$ on average) statements. Whereas for $k=10$, \combpar{k}
achieves a mean improvement of $19$ ($13.35\%$ on average) statements
on the ranking and a maximum ranking improvement
of $209$ ($73.7\%$ on average) statements. Such difference is justified by the fact that
entire files are discarded in \combpar{5}, whose statements are
included in the ranking of \combpar{10}. Consequently, the
improvements obtained by the technique will not be as high if slicing
on these additional files is unable to aggressively and safely discard
statements. This also shows that slicing files, in addition to slicing
statements from those files, is very beneficial for fault localization
performance.

@@

\begin{figure}[h]
	\vspace{-1cm}
		\includegraphics[width=0.45\textwidth]{figures/heatmap_nemenyi_result.pdf}
		\caption{Siegel post-hoc analysis results}
		\label{fig:performance}
\end{figure}

@@

The main threat to internal validity lies in the complexity of several of the tools
used in our experiments, most notably the Lithium toolset, the SFL diagnosis tool,
and the implementation of \comb{}.
%
\section{Related Work}
\Rui{Introductory sentences should say something like: model-based software
debugging, from the DX community, has been shown to be similar to slicing
Mayer and Stumptner, 2008; Wotawa and Nica; etc. Having said that, not many
interesting techniques having been pursued because of scalability. We have
achieved it with a type of program slicing --- critical slicing. Next, we
visit the previous works on program slicing and SFL, without the idea of
being exhaustive, but merely discussing the works that we deem relevant for
this paper.}

\Rui{revisit sentences; check if recent papers are cited.}

\subsection{Program Slicing}

Program Slicing is an old technique with several applications in PL
and SE research~\cite{Weiser:1981:PS:800078.802557}. Slicing can be
implemented in different ways. Dynamic Slicing has found its main
application in fault
localization~\cite{Agrawal:1990:DPS:93542.93576}---in this application
context, failing tests exist. Research in this area has mainly focused
on slicing code
efficiently~\cite{Wang:2008:DSJ:1330017.1330021,Wang:2004:UCB:998675.999455}
and avoiding data and control omission
errors~\cite{Zhang:2007:TLE:1250734.1250782,Lin:2018:BDE:3238147.3238163}. Omission errors correspond to the
cases where tests fail because some part of the code was not executed
when it should. Dynamic fault localization techniques cannot hope to
soundly report bugs in those cases. The issue is that incorporating
static information to capture those cases can result in unacceptably
large slices, which defeats the purpose of reducing the fault search
space. It is worth noting that, conceptually, the \sfl{}+\ds{} combination
can be used with any form of dynamic slicing. We chose an
implementation of Critical
Slicing~\cite{DeMillo:1996:CSS:229000.226310} for its generality.

\subsection{SFL}

Statistics-based techniques (e.g., ~\cite{Pearson:2017:EIF:3097368.3097441}) are
popular automated fault localization techniques within the Software Engineering
community. They correlate information about program fragments that have been
exercised in multiple program execution traces (also called \textit{program
spectra}) with information about successful and failing executions. By doing
that, statistics-based approaches yield a list of suspect program fragments
sorted by their likelihood to be at fault. Since this technique is efficient in
practice, it is attractive for large modern software systems ~\cite{Zoeteweij:2007:DES:1251988.1253298}.

Spectrum-based fault localization (\sfl{}) is amongst the most common statistical
fault localization technique that takes as input a test suite including at least
one failing test and reports on output a ranked list of components likely to be
in fault ~\cite{7390282,DBLP:conf/kbse/JonesH05,DBLP:journals/smr/LuciaLJTB14,DBLP:journals/jss/AbreuZGG09}.

\subsection{Combination of \sfl{} and Slicing}

Prior work has investigated the combination of dynamic slicing and
spectrum-based fault
localization ~\cite{Wotawa:2010:FLB:1848650.1849235,Alves:2011:FUD:2190078.2190115,DBLP:conf/ecai/HoferW12,lei-mao-dai-wang-2012,slicing-sfl-repair}. Although
the methodology used in these papers vary, the overall message is that
the combination is valuable. Note that slicing alone does not provide
the guarantee of improvement to \sfl{} as statements discarded with
slicing could have been ranked lower compared to faulty
statements. This paper differs from prior work in that it uses a much
larger dataset of programs and faults and a more rigorous experimental
methodology.
%
\section{Conclusions and Future Work}
\label{sec:conc}
%

Several approaches have been proposed in the literature to improve debugging
costs through automated software fault diagnosis to reduce time-to-market,
while maintaining high quality standards. In this domain, Dynamic Slicing (\ds)
and Spectrum-based Fault Localization (\sfl) are very popular fault diagnosis techniques and normally seen as complementary. \ds{} is This paper reports the outcome of
a study using real-world applications with the goal of demystifying the impact
of combining \ds~with \sfl. The results of our empirical study show that, in
practice, \ds~rarely misses faulty statements $9\%$ ($23$ misses in $260$ cases) and that
the \ds-\sfl~combination, coined as \combpar{k},
improves the diagnostic accuracy up to $73.7\%$ ($13.4\%$ on average).
Hence, we found that, despite tacit opinions of the research community about
the usefulness of \ds~in automated debugging, we found the combination practical
and effective, and encourage new \sfl~techniques to be evaluated against that
optimization.

>>>>

		\caption{Distribution of $\Delta{}C$ per variant when not considering
		test engineering problems and fault of omissions (left) and only considering
		the cases where \combpar{k} achieved improvement under one of the variants (right)}
		\label{fig:boxplot}
		\vspace{-0.2cm}

@@

In the following, we present statistical analysis to demonstrate that
the distributions of $C$ for each technique are different.
Table~\ref{table:st}, reports the average rank of all faulty
statements of the \dfj{} faults considered to the study after applying both
techniques, \sfl{}$^{k}$ and \combpar{k} for $k=5$ and $k=10$.
In bold, we present the results of the $227$ faults that do not comprise the
cases that are result of the limitations mentioned before (test design and fault 
of omission). These results show that \ds{} improves \sfl{} in a mean
of $6$ ($3.3\%$ on average) statements on the average ranking of all faulty statements, 
when considering $k=10$. Inside parentheses, we present the
rank results for all faults which do not report promissing results. However, 
if we only consider the faults which can benefit from our approach, we can observe that there is a considerable
amount of cases where the approach is actually successful. For
$k=5$, our approach achieves a mean improvement of $41.1$ ($9.57\%$ on average) statements
on the ranking and an impressive maximum ranking improvement
of $3171$ ($96.7\%$ on average) statements. Whereas for $k=10$, \combpar{k}
achieves a mean improvement of $19$ ($13.35\%$ on average) statements
on the ranking and a maximum ranking improvement
of $209$ ($73.7\%$ on average) statements. Such difference is justified by the fact that
entire files are discarded in \combpar{5}, whose statements are
included in the ranking of \combpar{10}. Consequently, the
improvements obtained by the technique will not be as high if slicing
on these additional files is unable to aggressively and safely discard
statements. This also shows that slicing files, in addition to slicing
statements from those files, is very beneficial for fault localization
performance.

@@

\begin{figure}[h]
	\vspace{-1.8cm}
		\includegraphics[width=0.45\textwidth]{figures/heatmap_nemenyi_result.pdf}
		\caption{Siegel post-hoc analysis results}
		\label{fig:performance}
		\vspace{-0.3cm}
\end{figure}

@@

The main threat to internal validity lies in the complexity of several of the tools
used in our experiments, most notably the Lithium toolset, the SFL diagnosis tool,
and the implementation of \comb{}.
%
\section{Related Work}

% \Rui{Introductory sentences should say something like: model-based software
% debugging, from the DX community, has been shown to be similar to slicing
% Mayer and Stumptner, 2008; Wotawa and Nica; etc. Having said that, not many
% interesting techniques having been pursued because of scalability. We have
% achieved it with a type of program slicing --- critical slicing. Next, we
% visit the previous works on program slicing and SFL, without the idea of
% being exhaustive, but merely discussing the works that we deem relevant for
% this paper.}
%
% \Rui{revisit sentences; check if recent papers are cited.}

% \subsection{Program Slicing}
%
% Program Slicing is an old technique with several applications in PL
% and SE research~\cite{Weiser:1981:PS:800078.802557}. Slicing can be
% implemented in different ways. Dynamic Slicing has found its main
% application in fault
% localization~\cite{Agrawal:1990:DPS:93542.93576}---in this application
% context, failing tests exist. Research in this area has mainly focused
% on slicing code
% efficiently~\cite{Wang:2008:DSJ:1330017.1330021,Wang:2004:UCB:998675.999455}
% and avoiding data and control omission
% errors~\cite{Zhang:2007:TLE:1250734.1250782,Lin:2018:BDE:3238147.3238163}. Omission errors correspond to the
% cases where tests fail because some part of the code was not executed
% when it should. Dynamic fault localization techniques cannot hope to
% soundly report bugs in those cases. The issue is that incorporating
% static information to capture those cases can result in unacceptably
% large slices, which defeats the purpose of reducing the fault search
% space. It is worth noting that, conceptually, the \sfl{}+\ds{} combination
% can be used with any form of dynamic slicing. We chose an
% implementation of Critical
% Slicing~\cite{DeMillo:1996:CSS:229000.226310} for its generality.
%
%
% \subsection{SFL}
%
% Statistics-based techniques (e.g., ~\cite{Pearson:2017:EIF:3097368.3097441}) are
% popular automated fault localization techniques within the Software Engineering
% community. They correlate information about program fragments that have been
% exercised in multiple program execution traces (also called \textit{program
% spectra}) with information about successful and failing executions. By doing
% that, statistics-based approaches yield a list of suspect program fragments
% sorted by their likelihood to be at fault. Since this technique is efficient in
% practice, it is attractive for large modern software systems ~\cite{Zoeteweij:2007:DES:1251988.1253298}.
%
% Spectrum-based fault localization (\sfl{}) is amongst the most common statistical
% fault localization technique that takes as input a test suite including at least
% one failing test and reports on output a ranked list of components likely to be
% in fault ~\cite{7390282,DBLP:conf/kbse/JonesH05,DBLP:journals/smr/LuciaLJTB14,DBLP:journals/jss/AbreuZGG09}.
%
% \subsection{Combination of \sfl{} and Slicing}
%
% Prior work has investigated the combination of dynamic slicing and
% spectrum-based fault
% localization ~\cite{Wotawa:2010:FLB:1848650.1849235,Alves:2011:FUD:2190078.2190115,DBLP:conf/ecai/HoferW12,lei-mao-dai-wang-2012,slicing-sfl-repair}. Although
% the methodology used in these papers vary, the overall message is that
% the combination is valuable. Note that slicing alone does not provide
% the guarantee of improvement to \sfl{} as statements discarded with
% slicing could have been ranked lower compared to faulty
% statements. This paper differs from prior work in that it uses a much
% larger dataset of programs and faults and a more rigorous experimental
% methodology.
% %
\section{Conclusions and Future Work}
\label{sec:conc}
%

Several approaches have been proposed in the literature to improve debugging
costs through automated software fault diagnosis to reduce time-to-market,
while maintaining high quality standards. In this domain, Dynamic Slicing (\ds)
and Spectrum-based Fault Localization (\sfl) are very popular fault diagnosis techniques and normally seen as complementary. This paper reports the outcome of
a study using real-world applications with the goal of demystifying the impact
of combining \ds~with \sfl. The results of our empirical study show that, in
practice, \ds~rarely misses faulty statements $9\%$ ($23$ misses in $260$ cases) and that
the \ds-\sfl~combination, coined as \combpar{k},
improves the diagnostic accuracy up to $73.7\%$ ($13.4\%$ on average).
Hence, we found that, despite tacit opinions of the research community about
the usefulness of \ds~in automated debugging, we found the combination practical
and effective, and encourage new \sfl~techniques to be evaluated against that
optimization.
